---
pagetitle: "Danilo Toapanta - DEV"
title: ''
code-fold: true
css: index.css
---

:::{.center .show-anchor-link}
## Dev {.unlisted .unnumbered }
:::

In this section I have recompiled the sources, links and all the material that were more helpfull during the creation of this website.

::: {.callout-important collapse="false"}
## Note about this page

- As the website has reached a moderate level of structure of my liking this page will be archived and instead used only for future references.
:::

::: {.to-do}

### To do{.unnumbered .unlisted}

<p>📄 Landing Page</p>

- [x] Include News Feed

<p>📄 About</p>

- [x] Take picture and place it in About
- [x] Contact form/ Details
- [x] Update the links i.e. 'Message me'
- [x] Add an extra page called 'now' to link to [`What I am doing now`]{.codeColored}
- [x] Link [`recent post`]{.codeColored} to a recent post
- [ ] Add CV to drive like [this](https://www.dropbox.com/s/mylkuexn11rlifg/R%C3%A9sum%C3%A9%E2%80%94Nono.MA.pdf?dl=0)

<p>📄 Blogs</p>

- [x] ~~Insert on top of page most visited blog~~ - *Keep it simple*

<p>📄 Projects</p>

- [x] Update projects from CV
- [ ] Embed the BSc thesis [slides](https://meghan.rbind.io/talk/rstudioconf/)

<p>📄 Sites</p>
- [x] Create grid to show all my site
- [ ] Create subdomains

<p>{{< fa code-branch size=xs >}} Deployment</p>

- [x] See integration with Github
- [x] Get a domain

<p>{{< fa brands sass size=xs >}} Styling</p>

- [x] Comment css sniptes in both themes
- [x] Arrange better the snipets in DEV section
- [x] Make integration mobile version (the hamburger icon)

<p>{{< fa wand-magic-sparkles size=2xs >}} Features to implement</p>

- [x] Add an extra page for 'Books'
- [x] Create scrollable box for links (show only fixed square)
- [x] Add button to lead to Github project
- [x] Click button to download a pdf version  of the current page
- [x] ~~Heart button if you find this blog usefull i.e people find this usefull~~ - *Keep it simple*
:::



::: {.panel-tabset}

## Useful Snippets

:::{.scrollableBox}
###### Fontawesome [Search FA icons](https://fontawesome.com/search?o=r&m=free)

```{text}
{{< fa thumbs-up >}}
{{< fa brands sass >}}
{{< fa brands sass size=xs >}}
```

Extension at: [link](https://github.com/quarto-ext)

###### Insert Twitter

```{r}
#| eval: false
#| code-fold: true
### Tweet {.unlisted .unnumbered}
    ```{html}
        <blockquote class="twitter-tweet"><p lang="en" dir="ltr">Deployment of <a href="https://twitter.com/Arabsat?ref_src=twsrc%5Etfw">@Arabsat</a> BADR-8 confirmed <a href="https://t.co/97VMx9aaD6">pic.twitter.com/97VMx9aaD6</a></p>&mdash; SpaceX (@SpaceX) <a href="https://twitter.com/SpaceX/status/1662324844497883136?ref_src=twsrc%5Etfw">May 27, 2023</a></blockquote> <script async src="https://platform.twitter.com/widgets.js" charset="utf-8"></script>
    ```
```

###### Use variables in text

```{=html}
<details><summary>Code</summary><blockquote>

Hello world! See [HTML details tag - W3Schools](https://www.w3schools.com/TAGS/tag_details.asp) for more info :)

</details>
```

###### To create collapsable code

```{=html}
<details><summary>Code</summary><blockquote>

    <!-- ```{{html}} -->
        <details open><summary>Hello</summary><blockquote>
          <details><summary>World - click me to open</summary><blockquote>
            :smile:
          </blockquote></details>
          <details open><summary>World</summary><blockquote>
            :smile:
          </blockquote></details>
        </blockquote></details>
    <!-- ``` -->

</details>
```
###### Insert variables in text

```{text}
    ```{r}
    #| code-fold: false
    #| eval: false
    #| echo: false
    x <- 5
    "x is `r x`" # here I need to use ""
    ```
```

###### To write Date:

```{text}
`r Sys.Date()`
```


###### To add some small spaces:
`<pre></pre>`

###### Too show step by step what you click on:

```{text}
Scribe: 
https://scribehow.com/
```

:::


## Important Links

:::{.scrollableBox}

###### Documentation

[Bootstrap](https://github.com/twbs/bootstrap/blob/main/scss/_variables.scss)

[QMD Presentations](https://github.com/rladies/meetup-presentations_freiburg/tree/master/2022-06-02_Quarto)

[Dates](https://quarto.org/docs/reference/dates.html)

[Example Jupyter Book](https://uwdata.github.io/visualization-curriculum/altair_marks_encoding.html)

[Example blog](https://stephenleo.github.io/data-science-blog/data-science-blog/python/python.html)

###### CSS, Layout, JS

[Quarto Layout](https://quarto.org/docs/output-formats/page-layout.html)

[Tutorial mystyles.css](https://ucsb-meds.github.io/customizing-quarto-websites/#/use-sass-colors)

[Article Layout](https://quarto.org/docs/authoring/article-layout.html)

[To Justify the text](https://stackoverflow.com/questions/74336124/how-to-justify-text-in-quarto)

[Condtional if](https://help.retentionscience.com/hc/en-us/articles/115003025814-How-To-Build-HTML-for-Conditional-Statements)

[Blocks Notes](https://quarto.org/docs/authoring/callouts.html)

[Pandoc](https://pandoc.org/MANUAL.html#exit-codes)

[Rmarkdown Basics](https://rmarkdown.rstudio.com/lesson-8.html)

[Code Chunks](https://bookdown.org/yihui/rmarkdown-cookbook/r-code.html)

[HTML editor](https://html5-editor.net/)

[Quarto Listing](https://quarto.org/docs/websites/website-listings.html)

[Pop up New Tab](https://stackoverflow.com/questions/56797898/rmarkdown-html-site-yml-navbar-href-links-open-in-new-tab-with-target-blank)

[Pandoc External Links](https://pandoc.org/MANUAL.html#extension-link_attributes)

[How to insert Google forms](https://handsondataviz.org/forms.html)

[To upload external videos](https://imgix.com/)

[To add comment sections on Blog](https://utteranc.es/)

[To create beautiful code to share](https://carbon.now.sh/)

[Links Js New Tab](https://stackoverflow.com/questions/56797898/rmarkdown-html-site-yml-navbar-href-links-open-in-new-tab-with-target-blank)

[Use Global Variables](https://quarto.org/docs/authoring/variables.html)

[How to add an audio file and add it](https://mine-cr.com/about/)

[Dimensions iPhones Inspector](https://github.com/amirshnll/custom-device-emulation-chrome)

[TOC idea](https://gjkoplik.github.io/spectral_clustering/#spectral_clustering)


###### Gallery {.unlisted .unnumbered}

[Links EJs](https://github.com/quarto-dev/quarto-web/blob/main/ejs/links.ejs)

[Gallery EJs Example](https://github.com/quarto-dev/quarto-web/blob/main/docs/gallery/gallery.yml)

[Talks about blocks and ::: ](https://robertmitchellv.com/blog/2022-08-building-with-quarto/building-with-quarto.html)

[For Examples of EJS Listing galleries](https://github.com/kazuyanagimoto/kazuyanagimoto.github.io/blob/main/static/html/research/work-in-progress.ejs)

###### Related to title page {.unlisted .unnumbered}

[link 1](https://github.com/quarto-dev/quarto-cli/discussions/1736)

[link 2](https://github.com/quarto-dev/quarto-cli/discussions/5260)

[link 3](https://quarto.org/docs/reference/formats/html.html#metadata)


###### Extensions: {.unlisted .unnumbered}

[Collapsable Social media](https://github.com/shafayetShafee/collapse-social-embeds)


###### Equations {.unlisted .unnumbered}

[Katex, used for rendering math equations fast](https://katex.org/docs/api.html)


###### Youtube Links {.unlisted .unnumbered}

[Daniel Chen - Install Python. Quarto Render All the Things | PyData NYC 2022](https://youtu.be/AnrGW8zoLx8)

[R-Ladies Freiburg (English) - Getting to know Quarto](https://youtu.be/shVSmYna3GM)

[Get started with Quarto | Mine Çetinkaya-Rundel](https://youtu.be/_f3latmOhew)


###### Redirects

[Change slug](https://blog.djnavarro.net/posts/2022-04-20_porting-to-quarto/#notes-on-yaml-headers)

[Redirects Slugs](https://github.com/EllaKaye/ellakaye.co.uk/blob/main/index.qmd)

[Quarto DOCs Redirect](https://quarto.org/docs/websites/website-navigation.html#redirects)

[Discussion](https://github.com/quarto-dev/quarto-cli/discussions/5384)

:::

:::







